S2. Additional figures and table

### 2022-02-19 Manuscript/S2.Additional_outputs.tex
update for arxiv submission

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={S2. Additional figures and table},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{S2. Additional figures and table}
\author{}
\date{\vspace{-2.5em}2021-10-25}

@@

\begin{figure}
\centering
\includegraphics{S2.Additional_outputs_files/figure-latex/posterior distributions-1.pdf}
\caption{Figure 1. Mixture predictive distribution of the probability of
a positive match, grouped by labelling status.}
\end{figure}

@@

\caption{\label{tab:var imp}Table 1. Term importance at the end of Session 1.}

@@

\begin{tabular}[t]{llrrll}

@@

Abstract & Transfer & 57.0 & 3.93 & 22.5 & 15.4\\

@@

Abstract & Network & Patient & 54.2 & 4.66 & 26.3 & 15.2\\

@@

Abstract & Worker & 50.0 & 3.33 & 0.421 & -1.21\\

@@

Abstract & Movement & 47.8 & 2.70 & 27.2 & 15\\

@@

Abstract & Facility & 45.0 & 2.22 & 19.6 & 14.8\\

@@

Abstract & Conduct & 42.6 & 3.70 & 0.221 & -2.57\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42.0} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\

@@

\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39.0} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\

@@

Abstract & California & 37.3 & 2.60 & 38 & 12.6\\

@@

Keyword & Patient Transfer | Patient Transfer & Patient Transport & 36.6 & 2.16 & 164 & 2\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{2.4e-07} & \cellcolor{gray!6}{-0.0415}\\
Abstract & Disease & 28.0 & 2.42 & 0.365 & -3.7\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare} & \cellcolor{gray!6}{Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\

@@

\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25.0} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\

@@

Abstract & Clinical & 23.6 & 2.10 & 0.421 & -2.9\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22.0} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\

@@

\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection} & \cellcolor{gray!6}{Humans} & \cellcolor{gray!6}{Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.40} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\

@@

\caption{\label{tab:var imp}Table 2. Term importance at the end of Session 2.}

@@

\caption{\label{tab:hyperparameters}Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.}
\begin{tabular}[t]{llllllllllll}
Cluster (mean score) & Num. iterations & Positive matches & Reviewed records & Sensitivity & Efficiency & Score (Sens. x Eff.) & Num. ensemble models & Uncertainty interval & Resampling & Num. initial training records & Positives oversampling multiplier\\
\cellcolor{gray!6}{1. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
2. Mult = 10,20 & Mods = 10,20,40,60 & Resamp = y & Init = 250,500 & Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
\cellcolor{gray!6}{3. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
4. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
\cellcolor{gray!6}{5. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
6. Mult = 10,20 & Mods = 1,5 & Resamp = n & Mods = 1 & Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
\cellcolor{gray!6}{7. Mult = 10,20} & \cellcolor{gray!6}{Mods = 10,20,40,60} & \cellcolor{gray!6}{Resamp = y} & \cellcolor{gray!6}{Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
8. Mult = 1 & Init = 250,500 & Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
\cellcolor{gray!6}{9. Mult = 10,20} & \cellcolor{gray!6}{Mods = 1,5} & \cellcolor{gray!6}{Resamp = n} & \cellcolor{gray!6}{Mods = 1} & \cellcolor{gray!6}{Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
10. Mult = 10,20 & Mods = 1,5 & Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
\cellcolor{gray!6}{11. Mult = 1} & \cellcolor{gray!6}{Init = 250,500} & \cellcolor{gray!6}{Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
12. Mult = 1 & Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{S2. Additional figures and table}
\author{}
\date{\vspace{-2.5em}2022-02-19}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={S2. Additional figures and table},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{lineno}
\linenumbers
\captionsetup[table]{labelformat=empty}
\captionsetup[figure]{labelformat=empty}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{figure}
\centering
\includegraphics{S2.Additional_outputs_files/figure-latex/posterior_distributions-1.pdf}
\caption{\textbf{Figure 1}. Mixture predictive distribution of the
probability of a positive match, grouped by labelling status.}
\end{figure}

@@

\caption{\label{tab:var imp}\textbf{Table 1}. Term importance at the end of Session 1.}

@@

\begin{tabular}[t]{llllll}

@@

Abstract & Transfer & 57 & 3.93 & 22.5 & 15.4\\

@@

Abstract & Network \& Patient & 54.2 & 4.66 & 26.3 & 15.2\\

@@

Abstract & Worker & 50 & 3.33 & 0.421 & -1.21\\

@@

Abstract & Movement & 47.8 & 2.7 & 27.2 & 15\\

@@

Abstract & Facility & 45 & 2.22 & 19.6 & 14.8\\

@@

Abstract & Conduct & 42.6 & 3.7 & 0.221 & -2.57\\
\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Patient} & \cellcolor{gray!6}{42} & \cellcolor{gray!6}{3.61} & \cellcolor{gray!6}{27.6} & \cellcolor{gray!6}{7.23}\\

@@

\cellcolor{gray!6}{Title} & \cellcolor{gray!6}{Hospital} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{1.95} & \cellcolor{gray!6}{12.5} & \cellcolor{gray!6}{12.5}\\

@@

Abstract & California & 37.3 & 2.6 & 38 & 12.6\\

@@

Keyword & Patient Transfer | Patient Transfer \& Patient Transport & 36.6 & 2.16 & 164 & 2\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Gene} & \cellcolor{gray!6}{28.3} & \cellcolor{gray!6}{1.29} & \cellcolor{gray!6}{0.00000024} & \cellcolor{gray!6}{-0.0415}\\
Abstract & Disease & 28 & 2.42 & 0.365 & -3.7\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Healthcare \& Facility} & \cellcolor{gray!6}{26.2} & \cellcolor{gray!6}{1.74} & \cellcolor{gray!6}{34.9} & \cellcolor{gray!6}{17}\\

@@

\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{System} & \cellcolor{gray!6}{25} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{11.9} & \cellcolor{gray!6}{3.47}\\

@@

Abstract & Clinical & 23.6 & 2.1 & 0.421 & -2.9\\

@@

\cellcolor{gray!6}{Abstract} & \cellcolor{gray!6}{Hand} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{1.97} & \cellcolor{gray!6}{0.822} & \cellcolor{gray!6}{-0.335}\\

@@

\cellcolor{gray!6}{Keyword} & \cellcolor{gray!6}{Cross Infection \& Humans \& Transmission} & \cellcolor{gray!6}{21.7} & \cellcolor{gray!6}{1.4} & \cellcolor{gray!6}{31.1} & \cellcolor{gray!6}{15.5}\\

@@

\caption{\label{tab:var imp}\textbf{Table 2}. Term importance at the end of Session 2.}

@@

\caption{\label{tab:hyperparameters}\textbf{Table 3}. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllllllll}
\toprule
Cluster (mean score) & Num. iterations & Positive matches & Reviewed records & Sensitivity & Efficiency & Score (Sens. x Eff.) & Num. ensemble models & Uncertainty interval & Resampling & Num. initial training records & Positives oversampling multiplier\\
\midrule
\cellcolor{gray!6}{1. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 100,250 (0.64)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{462 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{61.5\%} & \cellcolor{gray!6}{0.608} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
2. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 20,40,60 (0.56) & 5 & 82 / 82 & 618 / 1200 & 100\% & 48.5\% & 0.485 & 20 & 80 & y & 250 & 10\\
\cellcolor{gray!6}{3. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = n \& Init = 50,500 (0.5)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{81 / 82} & \cellcolor{gray!6}{589 / 1200} & \cellcolor{gray!6}{98.8\%} & \cellcolor{gray!6}{50.9\%} & \cellcolor{gray!6}{0.503} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{98} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{10}\\
4. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 5 (0.47) & 8 & 82 / 82 & 1123 / 1200 & 100\% & 6.42\% & 0.0642 & 5 & 98 & n & 50 & 10\\
\cellcolor{gray!6}{5. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 250,500 \& Mods = 10 (0.39)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{685 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{42.9\%} & \cellcolor{gray!6}{0.429} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{80} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{250} & \cellcolor{gray!6}{10}\\
\addlinespace
6. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 250,500 (0.31) & 5 & 82 / 82 & 874 / 1200 & 100\% & 27.2\% & 0.272 & 1 & 90 & n & 250 & 10\\
\cellcolor{gray!6}{7. Mult = 10,20 \& Mods = 10,20,40,60 \& Resamp = y \& Init = 50,100 (0.23)} & \cellcolor{gray!6}{7} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{948 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{21\%} & \cellcolor{gray!6}{0.21} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
8. Mult = 1 \& Init = 250,500 \& Mods = 20,40,60 (0.21) & 5 & 82 / 82 & 806 / 1200 & 100\% & 32.8\% & 0.328 & 60 & 80 & y & 250 & 1\\
\cellcolor{gray!6}{9. Mult = 10,20 \& Mods = 1,5 \& Resamp = n \& Mods = 1 \& Init = 50,100 (0.078)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{1139 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{5.08\%} & \cellcolor{gray!6}{0.0508} & \cellcolor{gray!6}{1} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{n} & \cellcolor{gray!6}{50} & \cellcolor{gray!6}{20}\\
10. Mult = 10,20 \& Mods = 1,5 \& Resamp = y (0.054) & 5 & 82 / 82 & 832 / 1200 & 100\% & 30.7\% & 0.307 & 5 & 80 & y & 250 & 20\\
\addlinespace
\cellcolor{gray!6}{11. Mult = 1 \& Init = 250,500 \& Mods = 1,5,10 (0.025)} & \cellcolor{gray!6}{5} & \cellcolor{gray!6}{82 / 82} & \cellcolor{gray!6}{981 / 1200} & \cellcolor{gray!6}{100\%} & \cellcolor{gray!6}{18.2\%} & \cellcolor{gray!6}{0.182} & \cellcolor{gray!6}{10} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{y} & \cellcolor{gray!6}{500} & \cellcolor{gray!6}{1}\\
12. Mult = 1 \& Init = 50,100 (0.0045) & 6 & 82 / 82 & 1151 / 1200 & 100\% & 4.08\% & 0.0408 & 20 & 80 & y & 50 & 1\\
\bottomrule
\end{tabular}}
\end{table}
